\hypertarget{features-and-structure-of-the-model}{%
\subsection{Features and structure of the
model}\label{features-and-structure-of-the-model}}

\hypertarget{basic-features-of-the-model.}{%
\subsubsection{Basic Features of the
Model.}\label{basic-features-of-the-model.}}

The CCSR/NIES AGCM is a physical description of the global
three-dimensional atmosphere, It is a numerical model for computing the
time evolution of a system as an initial value problem.

The data to be inputted are as follows.

\begin{itemize}
\item
  Initial data for each forecast variable (horizontal wind speed,
  temperature, surface pressure, specific humidity, cloud liquid water
  content, and surface volume)
\item
  Boundary condition data (surface elevation, surface condition, sea
  surface temperature, etc.)
\item
  Various parameters of the model (atmospheric components, physical
  process parameters, etc.)
\end{itemize}

On the other hand, the output looks like the following.

\begin{itemize}
\item
  Data for each forecast parameter and diagnostic parameter, for each
  time or time average
\item
  Initial data to be used for continuous execution (restart data)
\item
  Progress and various diagnostic messages
\end{itemize}

Here, the predictor variable is the differential equation of time
evolution, which is integrated in time by The data is obtained as a time
series, A diagnostic variable is defined as a set of predictor
variables, boundary conditions and parameters It is a quantity
calculated by some method that does not include time integration.

To be more specific , The model is basically a solution to the following
equation (the prediction equation).

\begin{quote}
\protect\hypertarget{struct:u-eq-1}{}{\textbackslash{[}struct:u-eq-1{]}}
\end{quote}

\begin{eqnarray}
  \frac{\partial u}{\partial t}  =  \left( {\mathcal F}_x \right)_D + \left( {\mathcal F}_x \right)_P
   \\
  \frac{\partial v}{\partial t}  =  \left( {\mathcal F}_y \right)_D + \left( {\mathcal F}_y \right)_P \\
  \frac{\partial T}{\partial t}  =  \left( Q \right)_D + \left( Q \right)_P \\
  \frac{\partial p_S}{\partial t}  =  \left( M \right)_D + \left( M \right)_P \\
  \frac{\partial q}{\partial t}  =  \left( S \right)_D + \left( S \right)_P \\
  \frac{\partial T_g}{\partial t}  =  \left( Q_g \right)_D + \left( Q_g \right)_P
\end{eqnarray}

Where, \(u,v,T,p_S,q,T_g\), \(u,v,T,p_S,q,T_g\) is, Easterly wind,
north-south wind, temperature, surface pressure, specific humidity,
etc., respectively It is a forecast variable with a two- or
three-dimensional distribution, such as The right-hand side is the term
that gives rise to the time variation of each of those forecast
variables. This time-varying term
\({\mathcal F}_x,{\mathcal F}_y,Q,S,Q_g\) is , It is calculated based on
the predictor variables \(u,v,T,p_S,q,T_g\), Advection due to
atmospheric motion represented by \(u\) and \(v\) (in the above equation
." in section \(D\)) and , The term ``cloud and radiation'' can be
broadly divided into two categories: the term by each process, such as
cloud and radiation, and the term by each process (the term in the
appendix \(P\)). The former is called the dynamic process and the latter
is called the physical process.

The main part of the time-varying term of a mechanical process is the
advection term, The accurate estimation of the spatial differentiation
is important in its calculation. In CCSR/NIES AGCM, the calculation of
the horizontal differential term We use spherical harmonic function
expansion. The physical processes, on the other hand, are energy
conversions due to the phase change of water and radiation absorption
and injection, The effects of small-scale atmospheric motion linked to
them, The effects of various processes on the surface of the earth,
including the effects of , Expressing with parameters in a simple model
(parameterization) is important.

The time integration of the predictive equation is ,
({[}construct:u-eq-1\en[construct:u-eq-1\end{eqnarray}](\#struct:u-eq-1)), etc. This
is done by approximating the left-hand side by a difference. For
example,

\begin{eqnarray}
  \frac{\partial q}{\partial t} \rightarrow \frac{q^{t+\Delta t} - q^{t}}{\Delta t}
\end{eqnarray}

By making ,

\begin{eqnarray}
  q^{t+\Delta t} = q^{t}
       + \Delta t \left[ \left( S \right)_D + \left( S \right)_P  \right]
\end{eqnarray}

\begin{quote}
\protect\hypertarget{struct:sabun}{}{\brahammer{[}struct:sabun{]}}.
\end{quote}

That would be. Here, \(S\) is a function of the forecast variables
\(u,v,T,p_S,q\), \(u,v,T,p_S,q\), etc. But.., Depending on which time
forecast variables are used in that calculation to evaluate \(S\), There
are various possible time difference schemes. In the CCSR/NIES AGCM ,
Euler method that uses the values from \(t\) as they are, The leap frog
method using the values from \(t+\Delta t/2\), The implicit method using
(approximate) values in \(t+\Delta t\) is used together.

In the CCSR/NIES AGCM The time integration of the predictors is done
separately for mechanical and physical processes. First, the mechanics
term is basically a leap frog,

\begin{eqnarray}
  \tilde{q}^{t+\Delta t} = q^{t-\Delta t} + 2 \Delta t \left( S \right)_D^{t}
\end{eqnarray}

However, some terms are treated as implicit. but some terms are treated
as implicit. In the physical process , Based on the results of
integrating the mechanics terms, Using a combination of the Euler and
implicit methods,

\begin{eqnarray}
  q^{t+\Delta t} = \tilde{q}^{t+\Delta t} + 2 \Delta t \left( S \right)_P
\end{eqnarray}

I'm looking for. Here,
(\protect\hyperlink{struct:sabun}{construct:sabun{]}}) \(\Delta t\).
Note that it has been replaced by \(2 \Delta t\).

\hypertarget{model-execution-flow.}{%
\subsubsection{Model Execution Flow.}\label{model-execution-flow.}}

The flow of model execution in brief is as follows. \is the name of the
relevant subroutine.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  set the parameters of the experiment, coordinates, etc.
  \texttt{MODULE:{[}SETPAR,PCONST,\ SETCOR,SETZS{]}}
\item
  read the initial values of the predictor variable
  \texttt{MODULE:{[}RDSTRT{]}}
\item
  start the time step \texttt{MODULE:{[}TIMSTP{]}}
\item
  perform time integration by mechanical processes
  \texttt{MODULE:{[}DYNMCS{]}}
\item
  perform time integration by physical processes
  \texttt{MODULE:{[}PHYSCS{]}}
\item
  advance the time \texttt{MODULE:{[}STPTIM,\ TFILT{]}}
\end{enumerate}

Output the data if necessary \texttt{MODULE:{[}HISTOU{]}}

Output the restart data if necessary \texttt{MODULE:{[}WRRSTR{]}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  3. Back to
\end{enumerate}

\hypertarget{predictive-variables.}{%
\subsubsection{Predictive variables.}\label{predictive-variables.}}

The predictor variables are as follows. Parentheses are the coordinate
system and \(\lambda,\varphi,\sigma, z\) are the coordinates,
respectively, Longitude, latitude, dimensionless pressure \(\sigma\),
indicating vertical depth. \The entries in the list are in units.

\begin{itemize}
\item
  TAB00000:0.0 east-west wind speed
\item
  TAB00000:0.1 \(u\) (\(\lambda,\varphi,\sigma\))
\item
  TAB00000:0.2 \The "m/score
\item
  TAB00000:1.0 north-south wind speed
\item
  TAB00000:1.1 \(v\) (\(\lambda,\varphi,\sigma\))
\item
  TAB00000:1.2 \The "m/score
\item
  TAB00000:2.0 atmospheric temperature
\item
  TAB00000:2.1 \(T\) (\(\lambda,\varphi,\sigma\))
\item
  TAB00000:2.2 \K.L.A.{[}K.R.I.E.D.{]}
\item
  TAB00000:3.0 surface pressure
\item
  TAB00000:3.1 \(p_S\) (\(\lambda,\varphi\))
\item
  TAB00000:3.2 The "hPa\textbackslash{}
\item
  TAB00000:4.0 specific humidity
\item
  TAB00000:4.1 \(q\) (\(\lambda,\varphi,\sigma\))
\item
  TAB00000:4.2 {[}kg/kg\textbackslash{]}
\item
  TAB00000:5.0 Cloud water mixing ratio
\item
  TAB00000:5.1 \(l\) (\(\lambda,\varphi,\sigma\))
\item
  TAB00000:5.2 {[}kg/kg\textbackslash{]}
\item
  TAB00000:6.0 underground temperature
\item
  TAB00000:6.1 \(T_g\) (\(\lambda,\varphi,z\))
\item
  TAB00000:6.2 \K.L.A.{[}K.R.I.E.D.{]}
\item
  TAB00000:7.0 subterranean moisture
\item
  TAB00000:7.1 \(W_g\) (\(\lambda,\varphi,z\))
\item
  TAB00000:7.2 \The "m/m\\
\item
  TAB00000: 8.0 amount of snowfall
\item
  TAB00000:8.1 \(W_y\) (\(\lambda,\varphi\))
\item
  TAB00000:8.2
\item
  TAB00000:9.0 sea-ice thickness
\item
  TAB00000:9.1 \(h_I\) (\(\lambda,\varphi\))
\item
  TAB00000:9.2
  \textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.25\textbackslash0.00\}.
\end{itemize}

However, the sea ice thickness is usually only a predictor in the
mixed-layer coupled model. In addition, the ground temperature is also
higher in the oceans not covered by sea ice Normally, it is not a
predictor variable. Also, in the CCSR/NIES AGCM, \(q\) and \(l\) are
independent Not a variable , In fact, \(q+l\) is the forecast variable.

Of these, The surface and subsurface related quantities
\(T_g, W_g, W_y, h_I\) are At the same time it only stores the amount of
one step, but, The atmospheric quantities \(u, v, T, p_S, q, l\) are,
You need to memorize the amount for two steps at a time. This means that
in the time integration of the dynamics of atmospheric quantities This
is because the leap forg method is used.

The atmospheric quantities \(u, v, T, p_S, q, l\) are , The main routine
is a variable administered by the main routine AGCM5. On the other hand,
the surface and subsurface quantities of \(T_g, W_g, W_y, h_I\) It
doesn't appear in the main routine, It is managed by the subroutine
\texttt{MODULE:{[}PHYSCS{]}}, which is a subroutine for physical
processes.

\hypertarget{the-flow-of-time-evolution-of-variables}{%
\subsubsection{The flow of time evolution of
variables}\label{the-flow-of-time-evolution-of-variables}}

We briefly summarize the flow of the model, focusing on the time
evolution of the predictor variables.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  read the initial value \texttt{MODULE:{[}RDSTRT,PRSTRT{]}}
\end{enumerate}

Initially, the quantities \(u, v, T, p_S, q, l\) related to the
atmosphere are essentially Two sets of quantities in \(t\) and
\(t-\Delta t\) must be prepared. This can be prepared if you are
starting from the output results of the previous model, but the It is
not possible to prepare for a departure from normal observations and
climate values. In that case, we start from the same value as the value
of the two time steps, Launch the calculation using the fine
\(\Delta t\) (see below for details).

The initial values for the atmospheric quantities \(u, v, T, p_S, q, l\)
are read from , This is done with \texttt{MODULE:{[}RDSTRT{]}}, called
by the main routine. On the other hand, the initial values of the
surface and underground quantities \(T_g, W_g, W_y, h_I\) are read from
In \texttt{MODULE:{[}PRSTRT{]}}, called by \texttt{MODULE:{[}PHYSCS{]}},
the This is done.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  start the time step \texttt{MODULE:{[}TIMSTP{]}}
\end{enumerate}

Forecast variables at time \(t\) (and partly in \(t-\Delta t\))
\(u^{t}, u^{t-\Delta t}, v^{t}, v^{t-\Delta t}, T^{t}, T^{t-\Delta t}, p_S^{t}, p_S^{t-\Delta t}, q^{t}, q^{t-\Delta t}, l^{t}, l^{t-\Delta t}, T_g^{t}, W_g^{t}, W_y^{t}\)
shall be complete.

\begin{verbatim}
 $\Delta t$ is essentially an externally given parameter,
\end{verbatim}

At regular intervals, the stability of the calculation is evaluated, If
there is a risk of calculation instability reduce the size of the
\(\Delta t\) \texttt{MODULE:{[}TIMSTP{]}}.

Set the output of the predictor variable \texttt{MODULE:{[}AHSTIN{]}}

In the atmospheric forecast variables, the output is usually The value
of time \(t\) at this stage
\(u^{t}, v^{t}, T^{t}, p_S^{t}, q^{t}, l^{t}\) It is. The actual output
is performed by the later \texttt{MODULE:{[}HISTOU{]}} The timing, which
is sent to the buffer here, is

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  mechanical processes \texttt{MODULE:{[}DYNMCS{]}}
\end{enumerate}

Solving for the time variation of the predicted variables due to
dynamical processes.
\(u^{t}, u^{t-\Delta t}, v^{t}, v^{t-\Delta t}, T^{t}, T^{t-\Delta t}, p_S^{t}, p_S^{t-\Delta t}, q^{t}, q^{t-\Delta t}, l^{t}, l^{t-\Delta t}\)
Based on , Value of the forecast variable in \(t+\Delta t\) considering
only mechanical processes
\(\hat{u}^{t+\Delta t}, \hat{v}^{t+\Delta t}, \hat{T}^{t+\Delta t}, \hat{p_S}^{t+\Delta t}, \hat{q}^{t+\Delta t}, \hat{l}^{t+\Delta t}\)
Ask for .

\begin{verbatim}
 1. convert to vorticity and divergence `MODULE:[UV2VDG, VIRTMD, HGRAD]`
\end{verbatim}

Atmospheric forecast parameters of \(u, v, T, p_S, q, l\) In order to
estimate the change term due to mechanical processes, we first need to
estimate \(u^{t}, v^{t}\) as the grid point values for vorticity and
divergence \(\zeta^{t},D^{t}\), Convert to \(\zeta^{t},D^{t}\). This is
because the equations of mechanics are written in terms of vorticity and
divergence. This transformation involves a spatial derivative, This can
be done precisely by using the spherical harmonic function expansion
\texttt{MODULE:{[}UV2VDG{]}}.

Furthermore, calculate the pseudotemperature \(T_v^{t}\), and then set
\texttt{MODULE:{[}VIRTMD{]}}, I still use the spherical harmonic
function expansion. Calculates the horizontal differential of surface
pressure \(\nabla \ln p_S\) \texttt{MODULE:{[}HGRAD{]}}.

\begin{verbatim}
 2. calculation of the time-varying term by advection `MODULE:[GRDDYN]`
\end{verbatim}

Using the values in \(t\) of \(u, v, T, p_S, q, l\), Due to horizontal
and vertical advection, Compute some of the time-varying terms for each
atmospheric variable. First, from the continuity equation, vertical
velocity \(\dot{\sigma}\) and To find the time variation term of \(p_S\)
diagnostically, Using it, calculate the vertical advection term for
\(u, v, T, q, l\). Furthermore, the horizontal advection fluxes of
\(u, v, T, q, l\) are calculated.

\begin{verbatim}
 3. convert to a spectrum `MODULE:[GD2WD, TENG2W]`
\end{verbatim}

Value of grid points in \(t-\Delta t\) for atmospheric forecast
parameters From \(u^{t}, v^{t}, T^{t}, p_S^{t}, q^{t}, l^{t}\), Values
in Spectral Space in Spherical Harmonic Function Expansion (However, the
vorticity is changed to divergence)
\(\tilde{\zeta}^{t}, \tilde{D}^{t}, \tilde{T}^{t}, \tilde{\pi}^{t}, \tilde{q}^{t}, \tilde{l}^{t}\)
(but, \(\pi \equiv \ln p_S\)) \texttt{MODULE:{[}GD2WD{]}}.

In addition, the vertical advection of \(u, v, T, p_S, q, l\) Expand the
time-varying term into a spectrum. Also, by using the derivative in
spectral space, Convergence of the horizontal advection flux is
calculated, MODULE:{[}TENG2W{]}` to add to the spectral representation
of the time change term.

This allows the \(\zeta, D, T, \pi, q, l\) Most terms in the
time-varying term are obtained as spectral values. However, among the
time-varying terms in \(\zeta, D, T, \pi\), The term that depends
linearly on horizontal divergence \(D\) is To do time integration by the
semi-implicit method, It is not included in the time-varying term at
this point.

\begin{verbatim}
 4. time integration `MODULE:[TINTGR]`
\end{verbatim}

Among the time-varying terms in \(\zeta, D, T, \pi\) , We have added a
linearly dependent term (the gravitational wave term) to the
horizontally diverging \(D\) Treat in the semi-implicit method, In
addition, the horizontal diffusion of \(\zeta, D, T, q, l\) By
implicitly incorporating the Perform time integration of the mechanical
process part. This allows for the Spectral representation of forecast
values
\(\tilde{\zeta}^{t+\Delta t}, \tilde{D}^{t+\Delta t}, \tilde{T}^{t+\Delta t}, \tilde{\pi}^{t+\Delta t}, \tilde{q}^{t+\Delta t}, \tilde{l}^{t+\Delta t}\)
is required.

\begin{verbatim}
 5. conversion to grid values `MODULE:[GENGD]`
\end{verbatim}

From the forecast variables in the spectral representation ,
\(u, v, T, p_S, q, l\), of \(t+\Delta t\) considering only mechanical
processes Grid point values for forecast values
\(\hat{u}^{t+\Delta t}, \hat{v}^{t+\Delta t}, \hat{T}^{t+\Delta t}, \hat{p_S}^{t+\Delta t}, \hat{q}^{t+\Delta t}, \hat{l}^{t+\Delta t}\)
.

\begin{verbatim}
 6. diffusion correction `MODULE:[CORDIF, CORFRC]`
\end{verbatim}

Horizontal diffusion is applied on the surface of \(\sigma\) and so on,
In large areas of mountain slopes, water vapor is transported uphill,
Causing problems such as bringing false precipitation at the top of the
mountain. To mitigate that, etc. such that the diffusion of the \(p\)
surface is close to Insert corrections for \(T,q,l\)
\texttt{MODULE:{[}\ CORDIF{]}}. CORDIF{]}`.

Also, heat from friction is added to \(\hat{T}\)
\texttt{MODULE:{[}CORFRC{]}}

\begin{verbatim}
 7. mass conservation correction `MODULE:[MASFIX]`
\end{verbatim}

Saving of the global integral values of \(q\) and \(l\) is satisfied,
and make corrections so that there will be no negative values in \(q\).
In addition, the correction is made so that the mass of the dry air is
constant.

When I left DYNMCS , The value of the forecast parameter in
\(t-\Delta t\) has been discarded, Overwritten by the value of the
forecast variable in \(t\). The area containing the \(t\) forecast
variable is , Only the mechanics process is considered. The value of the
forecast parameter in \(t+\Delta t\) is entered.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  physical process \texttt{MODULE:{[}PHYSCS{]}}
\end{enumerate}

Value of the predicted variables in \(t+\Delta t\) considering only
mechanical processes
\(\hat{u}^{t+\Delta t}, \hat{v}^{t+\Delta t}, \hat{T}^{t+\Delta t}, \hat{p_S}^{t+\Delta t}, \hat{q}^{t+\Delta t}, \hat{l}^{t+\Delta t}\)
and by adding a time-varying term from physical processes to The value
of the forecast parameter in \(t+\Delta t\)
\(u^{t+\Delta t}, v^{t+\Delta t}, T^{t+\Delta t}, p_S^{t+\Delta t}, q^{t+\Delta t}, l^{t+\Delta t}\)
Ask for .

\begin{verbatim}
 Calculation of the basic diagnostic variables `MODULE:[PSETUP]`
\end{verbatim}

The basic Find the diagnostic variables.

\begin{verbatim}
 2. cumulus convection, large-scale condensation `MODULE:[CUMLUS, LSCOND]`
\end{verbatim}

The time-varying terms of \(T, q, l\) due to cumulus convection are
found, and \texttt{MODULE\ :{[}CUMLUS{]}} Perform time integration with
\texttt{MODULE:{[}GDINTG{]}} just for that term. In addition, the
time-varying terms of \(T, q, l\) due to large-scale condensation and
\texttt{MODULE:{[}LSCOND{]}}, Perform time integration with
\texttt{MODULE:{[}GDINTG{]}} just for that term. Precipitation due to
cumulus convection and large scale condensation \(P_c, P_l\), Cloud
cover (\(C_c, C_l\), \(C_c, C_l\), etc.) is required. This makes
\(T, q, l\) Adjusted value for convective condensation process
\(\hat{T}^{t+\Delta t,a}, \hat{q}^{t+\Delta t,a}, \hat{l}^{t+\Delta t,a}\)
That would be.

\begin{verbatim}
 3. set the surface boundary condition `MODULE:[GNDSFC, GNDALB]`
\end{verbatim}

Set up the surface conditions with given data. The ground state index,
sea surface temperature, etc. are set to \texttt{MODULE:{[}GNDSFC{]}}.
Also, the surface albedo is set to be other than sea level
\texttt{MODULE:{[}GNDALB{]}}. (The calculation of sea-surface albedo has
been incorporated into the radiative flux calculation routine.)

\begin{verbatim}
 4. calculation of the radiation flux `MODULE:[RADCON, RADFLX]`
\end{verbatim}

Set the atmospheric data for radiation flux calculation
\texttt{MODULE:{[}RADCON{]}}. Normally, ozone is read from a file. Cloud
water and cloud cover are obtained by convection and large-scale
condensation, We can also give it to you from the outside here. Using
these and \(\hat{T}^{t+\Delta t,a}, \hat{q}^{t+\Delta t,a}\) Shortwave
and longwave radiation flux \(F_R\), and Calculates the differential
coefficient of surface temperature used for implicit calculation
\texttt{MODULE:{[}\ RADFLX{]}}. RADFLX{]}`.

\begin{verbatim}
 5. calculation of the vertical diffuse flux `MODULE:[VDFFLX, VFTND1]`

     $\hat{u}^{t+\Delta t}, \hat{v}^{t+\Delta t},
\end{verbatim}

\hat{T}\^{}\{t+\Delta t,a\}, \hat{q}\^{}\{t+\Delta t,a\},
\hat{l}\^{}\{t+\Delta t,a\}\$ with , Fluxes in \(u, v, T, q, l\) by
vertical diffusion and Calculate the differential coefficient for
implicit calculation \texttt{MODULE:{[}VDFFLX{]}}. In addition, the
implicit solution is computed in the middle with the LU decomposition of
\texttt{MODULE:{[}\ VFTND1{]}}. VFTND1{]}`.

\begin{verbatim}
 6. calculation of surface processes and time integration of underground variables `MODULE:[SURFCE]`
\end{verbatim}

Calculate the fluxes of \$u, v, T, q \$ between the earth's surface and
atmosphere, Considering the conduction of heat in the ground, the energy
balance at the surface is Solve with an implicit solution. This allows
the surface temperature (\(T_s\)) to be diagnostically determined and
Value of the ground temperature in the \(t+\Delta t\)
\(T_g^{t+\Delta t}\) is required. In addition, the rate of change of the
predicted variables for the first layer of the atmosphere Find
\(F_{x,1}, F_{y,1}, Q_1, S_1\).

Snow accumulation and snowmelt processes are taken into account, The
value of the snowpack in \(t+\Delta t\) is determined by
\(W_y^{t+\Delta t}\), Taking into account the movement of water in the
ground Ground moisture \(W_g^{t+\Delta t}\) is required.

In the case of the oceanic mixed layer model, the Ocean temperature and
sea ice thickness The value in \(t+\Delta t\) is found by time
integration.

\begin{verbatim}
 7. evaluation of time variation due to radiative and vertical diffusion `MODULE:[VFTND2, RADTND, FLXCOR]`
\end{verbatim}

Combined radiative flux and vertical diffusion The rate of change of
each forecast variable of the atmosphere over time. Seek
\({\mathcal F}_x, {\mathcal F}_y, Q, S\) \texttt{MODULE:{[}VFTND2{]}}.
In addition, isolate the contribution of the radiation from them
\texttt{MODULE:{[}RADTND{]}}. This is not directly used in the model,
but , For the convenience of the data output.

Because we use the implicit method in these calculations, due to changes
in surface temperature and atmospheric forecast variables. We are taking
into account changes in flux. We'll account for that and the fluxes that
break even. Calculate with \texttt{MODULE:{[}FLXCOR{]}}. This is also
for the convenience of data output.

\begin{verbatim}
 8. evaluation of gravitational wave resistance `MODULE:[GRAVTY]`
\end{verbatim}

Calculating the change in atmospheric momentum due to gravitational
waves originating from the terrain, Time Dependence of \(u, v\) by
Vertical Diffusion Add to \({\mathcal F}_x, {\mathcal F}_y\).

\begin{verbatim}
 9. evaluation of the atmospheric pressure change term
\end{verbatim}

Considering the changes in pressure due to precipitation and
evaporation, Find the atmospheric pressure change term \(M\).

\begin{verbatim}
 10. time integration of physical processes `MODULE:[GDINTG]`
\end{verbatim}

due to radiation, vertical diffusion, surface processes, gravitational
wave resistance, etc. The rate of change of each forecast variable of
the atmosphere over time. Using
\({\mathcal F}_x, {\mathcal F}_y, Q, M, S\), Find the value of
\(t+\Delta t\) by time integration.

\begin{verbatim}
 11. drying convection adjustment `MODULE:[DADJST]`
\end{verbatim}

If the calculated \(T, q, l\) are unstable for dry convection Drying
convection adjustment.

By the above procedure, Value of the forecast parameters in
\(t+\Delta t\)
\(u^{t+\Delta t}, v^{t+\Delta t}, T^{t+\Delta t}, p_S^{t+\Delta t}, q^{t+\Delta t}, l^{t+\Delta t}\)
is required.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  time filter \texttt{MODULE:{[}TFILT{]}}
\end{enumerate}

In order to prevent the leap frog from causing a calculation mode, Apply
a time filter. \(u^{t-\Delta t}, u^{t}, u^{t+\Delta t}\) The results of
the smoothing operation using the data at the three times of Operate on
each variable by replacing it with \(u^{t}\). (Actually, at the
\texttt{MODULE:{[}TFILT{]}} stage, the Since the information on
\(u^{t-\Delta t}\) has been erased, This operation is a two-step
process. The first stage of operation is done in the mechanical
process.)
