\hypertarget{drying-convection-regulation}{%
\subsection{Drying convection
regulation}\label{drying-convection-regulation}}

\hypertarget{overview-of-drying-convective-regulation}{%
\subsubsection{Overview of Drying Convective
Regulation}\label{overview-of-drying-convective-regulation}}

Drying convection control , Convective instability in the stratum
between two successive levels, In other words, if the temperature decay
rate is greater than the dry adiabatic decay rate The temperature
reduction rate is adjusted to the dry adiabatic reduction rate. Water
vapor and other substances are mixed in at this time. The main input
data are temperature \(T\) and specific humidity \(q\), The output data
is the adjusted air temperature \(T\) and specific humidity \(q\).

Essentially, if vertical diffusion is efficient, then The vertical
convective instability should be basically removed. However, it may be
in short supply in the stratosphere, A convection adjustment has been
added to stabilize the calculation.

\hypertarget{drying-convection-regulation-procedures.}{%
\subsubsection{Drying convection regulation
procedures.}\label{drying-convection-regulation-procedures.}}

The conditions for convective instability in the layers \((k-1,k)\) are

\begin{eqnarray}
\frac{T_{k-1} - T_{k}}{p_{k-1} - p_{k}} 
  > \frac{R}{C_p} \bar{T_{k-1/2}}
  = \frac{R}{C_p}
    \frac{\Delta p_{k-1} T_{k-1} + \Delta p_{k} T_{k}}
         {\Delta p_{k-1} + \Delta p_{k}} 
\end{eqnarray}

Namely,

\begin{eqnarray}
 S = T_{k-1} - T_{k}
     - \frac{R}{C_p} 
        \frac{\Delta p_{k-1} T_{k-1} + \Delta p_{k} T_{k}}
         {\Delta p_{k-1} + \Delta p_{k}} 
       (p_{k-1} - p_{k})
   > 0 
\end{eqnarray}

\begin{quote}
\protect\hypertarget{p-adj:cond}{}{p-adj{[}p-adj:cond\en{]}}.
\end{quote}

is a condition.

When this is satisfied ,

\begin{eqnarray}
T_{k-1}  \leftarrow  \frac{\Delta p_{k}}{\Delta p_{k-1} + \Delta p_{k}} S \\
T_{k}  \leftarrow  \frac{\Delta p_{k-1}}{\Delta p_{k-1} + \Delta p_{k}} S 
\end{eqnarray}

to compensate for the temperature. Furthermore,

\begin{eqnarray}
q_{k-1}, q_{k} \leftarrow
     \frac{\Delta p_{k-1} q_{k-1} + \Delta p_{k} q_{k}}
          {\Delta p_{k-1} + \Delta p_{k}} 
\end{eqnarray}

to average the values of specific humidity etc. in the two layers.

When you do this, The layers above and below it may become unstable.
That's why, Repeating this operation from the lower level to the upper
level. Repeat until there is no more layer of convective instability.
However, considering the calculation error and so on, (as a condition of
\protect\hyperlink{p-adj:condo}{\textbackslash p{[}p-adj:condo{]}}), It
is considered to have converged if S is less than or equal to some small
finite value that is not zero.

Currently, the standard adjustment is between the second and third layer
from the bottom and above.
