\hypertarget{fluxes-to-atmospheric-models}{%
\subsection{Fluxes to Atmospheric
Models}\label{fluxes-to-atmospheric-models}}

\hypertarget{fluxes-between-atmosphere-and-ocean}{%
\subsubsection{Fluxes between atmosphere and
ocean}\label{fluxes-between-atmosphere-and-ocean}}

Fluxes from the sea surface to the atmosphere (\(FLXO\)) are calculated
on the sea surface grid of the atmospheric model.

Boundary conditions such as sea surface temperature, sea ice
concentration, sea ice thickness, snow depth over sea ice, sea ice
internal temperature, and ocean surface current velocity are obtained
from the ocean model through an exchanger (sea ice surface temperature
is determined from the sea ice internal temperature, sea ice thickness,
and atmospheric conditions over the sea ice. The sea ice velocity is not
currently used for flux calculations in MIROC). The atmospheric boundary
conditions such as wind speed, temperature, and specific humidity at sea
are converted from the atmospheric grid to the sea surface grid using
linear or cubic spline completion. The fluxes from the sea surface are
calculated separately for seawater and sea ice, averaged by area weight,
and passed to the atmosphere. When using a sea ice model categorized by
sea ice thickness, it may be necessary to calculate fluxes for each sea
ice thickness category, but the current model specification calculates
fluxes for the average sea ice thickness. The conversion of fluxes and
boundary conditions between the atmosphere and ocean by the exchanger
will be described in detail later.

\hypertarget{fluxes-between-atmospheric-land-surfaces}{%
\subsubsection{Fluxes between atmospheric land
surfaces}\label{fluxes-between-atmospheric-land-surfaces}}

Fluxes from the land surface to the atmosphere (\(FLXL\)) are calculated
on a land surface grid. A land surface grid consists of multiple soil
covers and lakes. Freezing and thawing of lakes and snow cover are
considered by a vertical 1D ice model (0-layer model). If the area of
the land surface grid is \(SL\), the area occupied by the lake and each
soil cover is respectively

\begin{eqnarray} SL^{lake}=SL * LKFRC * FLND \end{eqnarray}

\begin{eqnarray} SL^{grd}_k = SL * GRFRC_k * (1-LKFRC) * FLND \end{eqnarray}

where \(LKFRC\) is the percentage of lakes on land, \(k\) is the type of
soil cover, and \(GRFRC_k\) is the percentage of soil cover \(k\) on
land excluding lakes. Fluxes from the land surface are calculated
separately over each of these soil covers and lakes, averaged by area
weight, and passed to the atmosphere.

\begin{eqnarray} FLXL = LKFRC * FLXL^{lake} + (1-LKFRC) * \sum_{k=1}^{km} (GRFRC_k * FLXL_k^{grd}) \end{eqnarray}

where \(FLXL^{lake}\) is the flux at the lake surface,
\(FLXL_{k}^{grd}\) is the flux at soil cover \(k\), and \(km\) is the
number of soil cover types.

\hypertarget{total-flux-to-the-atmosphere}{%
\subsubsection{Total flux to the
atmosphere}\label{total-flux-to-the-atmosphere}}

Since the river model has no area, the flux to the atmosphere (\(FLXA\))
can be obtained as a weighted average of the sea-land distribution of
the fluxes on the land grid (\(FLXL\)) and at the sea grid (\(FLXO\)) as
follows

\begin{eqnarray} FLXA = \frac{1}{SA} * [ \sum _ {j=1}^{jldiv} \sum_{i=1}^{ildiv}(SL _ {ij} * FLND^{land} _ {ij}*FLXL_{ij}) + \sum _ {j=1}^{jodiv}\sum _ {i=1}^{iodiv }(SO _ {ij} * (1-FLND^{oc} _ {ij}) * FLXO _ {ij})] \end{eqnarray}.

Fluxes computed in the atmospheric model, such as precipitation, are
also included in \(FLXL\) and \(FLXO\). In the case of such fluxes, all
the fluxes in the partitioned land and sea surface grids have the same
value as the corresponding grid.

\hypertarget{fluxes-between-land-surface-model-and-river-model}{%
\subsection{Fluxes between land surface model and river
model}\label{fluxes-between-land-surface-model-and-river-model}}

\hypertarget{fluxes-between-river-land-surfaces-and-the-river-model}{%
\subsubsection{Fluxes between river land surfaces and the river
model}\label{fluxes-between-river-land-surfaces-and-the-river-model}}

In the current specification of the model, the fluxes of water between
river and land surfaces deal only with the inflow of water from the
river to the lake (\(RUNIN\)), the outflow from the lake to the river
(\(RUNOFF\)), the inflow of water to the land surface at the inland
vanishing point (\(RUNIN\)), and the outflow of water overflowing the
soil to the river (\(RUNOFF\)). Here, the inland vanishing point
indicates the point where the endpoint of the river disappears, such as
in deserts. The water balance in the river model is divided into ice and
water. The ice in the river model corresponds to a pseudo-glacier. Here,
the phase change in the river model is not considered to guarantee the
conservation of melting heat. In addition, the flow rate of a river is
defined as the amount of water present in the river grid divided by its
area. Water and ice are transported downstream in the river model
according to the river channel network data. In the river model in
MIROC6, the river discharge at the inland vanishing point of the river
is scattered over the global ocean to obtain the water balance.

\hypertarget{water-runoff-from-land-surface}{%
\subsubsection{Water Runoff from Land
Surface}\label{water-runoff-from-land-surface}}

When each soil cover in the land surface grid can no longer hold water
or snow and ice, water or ice is passed from each soil model to the
river model through the coupler.

\begin{eqnarray} RUNOFF^{grd}_{all} =
    (1-LKFRC) * \sum_{k=1}^{km}(GFLRC_{k} * RUNOFF^{grd}_{k}) \end{eqnarray}

The details of the runoff from each soil cover can be found in the
documentation of the land surface model MATSIRO. In the lake model, when
the lake level or snow/ice thickness (\(H\)) exceeds a constant value
(\(H_c\)), the water flows out to the river at a time constant
\(\tau_h\)

\begin{eqnarray} RUNOFF^{lake} = LKFRC * \frac{(H-H_c)}{\tau_h},~~~~~~ (H>H_c) \end{eqnarray}

\begin{eqnarray} RUNOFF^{lake} = 0,~~~~~~~~~~ (H<H_c) \end{eqnarray}

The average runoff from the land surface is as follows.

\begin{eqnarray} RUNOFF^{land}_{all} = RUNOFF^{lake} + RUNOFF^{grd}_{all} \end{eqnarray}

When considering the average runoff volume of the land surface grid, it
is necessary to multiply the above equation by the percentage of land
surface \(FLND\). In the river model, \(RUNOFF^{land}_{all}\) is
converted to the river grid with the weight of sea-land distribution,
and the runoff amount \(RUNOFF^{riv}\) is used for calculation.

\hypertarget{runin-of-water-from-a-river-to-a-lake}{%
\subsubsection{Runin of water from a river to a
lake}\label{runin-of-water-from-a-river-to-a-lake}}

When a lake exists in the middle of a river channel, water flows into
the lake according to the river flow rate. In order to calculate the
amount of water flowing into the lake, the river flow \(GDRIV\) in the
river grid is converted to the river flow \(GDRIVL\) in the land surface
grid through the coupler. Here, \(GDRIVL\) is the amount normalized by
the area of the land surface grid. In the land surface grid, the river
inflow to the lake, \(RUNINN\), is defined by the river flow
(\(GDRIVL\)) and the time constant \(\tau\) as follows

\begin{eqnarray} RUNINN^{lake}=GDRIVL/\tau \end{eqnarray}.

Since the current specification only considers inflow from rivers to
lakes, except at the inland vanishing point, the average inflow at the
land surface is

\begin{eqnarray} RUNINN^{land}=RUNINN^{lake}*LKFRC \end{eqnarray}.

When there are multiple river grids corresponding to a land surface
grid, if the river water inflow to the land surface averaged over the
land surface grid is returned to the river grid using only the area
weights as in \(RUNOFF\), it is possible that more water will flow out
of the river than exists in the river grid. Therefore, we convert the
ratio of discharge to river flow from the land surface grid to the river
grid, and estimate the river discharge (inflow to the land surface) in
each river grid. The runoff ratio of the river flow to the land surface
grid is

\begin{eqnarray} RINN^{land}=RUNINN^{land}/GDRIVL \end{eqnarray}.

If the discharge rate converted to the river grid is \(RINN^{riv}\), the
discharge (inflow to the land surface) in the river grid is

\begin{eqnarray} RUNINN^{riv}=RINN^{riv}*GDRIV \end{eqnarray}.

\hypertarget{fluxes-to-the-ocean-model}{%
\subsection{Fluxes to the ocean model}\label{fluxes-to-the-ocean-model}}

\hypertarget{boundary-conditions-for-the-ocean-on-a-sea-level-grid}{%
\subsection{Boundary conditions for the ocean on a sea level
grid}\label{boundary-conditions-for-the-ocean-on-a-sea-level-grid}}

As mentioned above, the fluxes between the atmosphere and the ocean are
calculated on the sea level grid. In this section, we describe the
conversion from the ocean model grid to the sea surface grid. The
standard variables to be converted from the ocean model to the
atmospheric sea surface grid are sea surface temperature (\(SST\)), sea
ice concentration (\(AI\)), sea ice thickness (\(HI\)), snow depth over
sea ice (\(HSN\)), sea ice internal temperature (\(TI\)), and ocean
surface current velocity (\(UO,VO\)). In order to clarify which grid we
are dealing with in the future, variables in the ocean model grid will
be denoted by superscript \(OGCM\) and variables in the sea surface grid
by superscript \(oc\). In addition, the position in the ocean grid is
denoted by \(LO\) and the position in the sea surface grid by \(LC\).
The boundary condition of the ocean in the sea level grid is defined as
follows.

\begin{eqnarray} SST^{oc}(LC) = \sum_{N=1}^{IJO(LC)}[SST^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]/SOCNG(LC) \end{eqnarray}

\begin{eqnarray} AI^{oc}(LC) = \sum_{N=1}^{IJO(LC)}[AI^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]/SOCNG(LC) \end{eqnarray}

\begin{eqnarray} HI^{oc}(LC) = \frac{\sum_{N=1}^{IJO(LC)}[HI^{OGCM}(IJO2C(LC,N))*AI^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]/SOCNG(LC)} {SOCNG(LC)*AI^{oc}(LC)} \end{eqnarray}

\begin{eqnarray} HSN^{oc}(LC) = \frac{\sum_{N=1}^{IJO(LC)}[HSN^{OGCM}(IJO2C(LC,N))*AI^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]/SOCNG(LC)} {SOCNG(LC)*AI^{oc}(LC)} \end{eqnarray}

\begin{eqnarray} TI^{oc}(LC) = \frac{\sum_{N=1}^{IJO(LC)}[TI^{OGCM}(IJO2C(LC,N))*HI^{OGCM}(IJO2C(LC,N))*AI^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]/SOCNG(LC)} {SOCNG(LC)*HI^{oc}(LC)*AI^{oc}(LC)} \end{eqnarray}

\begin{eqnarray} UO^{oc}(LC)=RUO(LC)* \frac{\sum_{N=1}^{IJO(LC)}[UO^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]}{SOCNG(LC)}+RVO(LC)* \frac{\sum_{N=1}^{IJO(LC)}[VO^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]}{SOCNG(LC)} \end{eqnarray}

\begin{eqnarray} VO^{oc}(LC)=-RVO(LC)* \frac{\sum_{N=1}^{IJO(LC)}[UO^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]}{SOCNG(LC)}+RUO(LC)* \frac{\sum_{N=1}^{IJO(LC)}[VO^{OGCM}(IJO2C(LC,N))*SOCN(LC,N)]}{SOCNG(LC)} \end{eqnarray}

\begin{eqnarray} SOCNG(LC)= \sum_{N=1}^{IJO(LC)}SOCN(LC,N) \end{eqnarray}

where, \(IJO(LC)\): Number of ocean grids corresponding to the sea level
grid (\(LC\)) in the atmospheric node.

\(IJO2C(LC,N)\): Location of the ocean grid corresponding to the sea
surface grid in the atmospheric node.

\(SOCN(LC,N)\): Area of the ocean grid corresponding to the sea surface
grid in the atmospheric node.

\(RUO(LC)\): Cosine of the rotation angle of the vector.

\(RVO(LC)\): Sine of the rotation angle of the vector

\(SOCNG(LC)\): Area of ocean occupied by sea surface grid.

The ratio of land surface to the sea level grid is also defined as
follow.

\(FLND^{oc}=(1-SOCNG)/SO\)

where, \(SO\) is the area of sea surface grid.

The variables related to sea ice that are converted to the sea surface
grid are calculated as the average of variables categorized by sea ice
layer thickness (\(AIM,HIM,HSM,TIM\)) as follows.

\begin{eqnarray} AI^{OGCM} = \sum_{L=1}^{NIC} AIM^{OGCM}(L) \end{eqnarray}

\begin{eqnarray} HI^{OGCM} = \sum_{L=1}^{NIC} HIM^{OGCM}(L)*AIM^{OGCM}(L)/AI^{OGCM} \end{eqnarray}

\begin{eqnarray} HSN^{OGCM} = \sum_{L=1}^{NIC} HSM^{OGCM}(L)*AIM^{OGCM}(L)/AI^{OGCM} \end{eqnarray}

\begin{eqnarray} TI^{OGCM} = \sum_{L=1}^{NIC} TIM^{OGCM}(L)*AIM^{OGCM}(L)/(AI^{OGCM}*HI^{OGCM}) \end{eqnarray}

where, \(NIC\) is the number of category of sea ice.

\hypertarget{conversion-of-air-sea-fluxes-calculated-on-the-sea-surface-grid-to-the-ocean-grid}{%
\subsubsection{Conversion of air-sea fluxes calculated on the sea
surface grid to the ocean
grid}\label{conversion-of-air-sea-fluxes-calculated-on-the-sea-surface-grid-to-the-ocean-grid}}

Fluxes calculated on the sea surface grid are calculated at sea surface
and sea ice surface, respectively, and fluxes to the atmosphere are
calculated as

\begin{eqnarray} FLXO=(1-AI)*FLUXO+AI*FLUXI \end{eqnarray}

These fluxes are time-integrated by the flux coupler in the atmospheric
model with weights for sea surface and sea ice extent, and then
converted to the ocean grid by the coupled atmosphere-ocean time step
and passed to the ocean model.

\begin{eqnarray} FLUXOA^{OGCM}(LO) = ROCN(LO)*\sum_{N=1}^{IJA(LO)} [FLUXOA^{oc}(IJC2O(LO,N))*SATM(LO,N)]/SATMG(LO) \end{eqnarray}

\begin{eqnarray} FLUXIA^{OGCM}(LO) = ROCN(LO)*\sum_{N=1}^{IJA(LO)} [FLUXIA^{oc}(IJC2O(LO,N))*SATM(LO,N)]/SATMG(LO) \end{eqnarray}

\begin{eqnarray} SATMG(LO)=ROCN(LO)*\sum_{N=1}^{IJA(LO)} SATM(LO,N) \end{eqnarray}

\begin{eqnarray} ROCN(LO)=SATMG(LO)/S^{OGCM}(LO) \end{eqnarray}

\begin{eqnarray} FLUXOA^{oc}=(1-AI^{oc})*FLUXO^{oc} \end{eqnarray}

\begin{eqnarray} FLUXIA^{oc}=AI^{oc}*FLUXI^{oc} \end{eqnarray}

where, \(IJA(LO)\)：Number of sea level grids in the atmospheric model
corresponding to the ocean grid (\(LO\))

\(IJC2O(LO,N)\)：Location of the sea surface grid of the atmospheric
model corresponding to the ocean grid

\(SATM(LO,N)\)：Area of the sea surface grid of the atmospheric model
corresponding to the ocean grid

\(SATM(LO,N)=SOCN(LC,L),LC=IJC2O(LO,N),LO=IJO2C(LC,L)\)

\(S^{OGCM}(LO)\)：Area of the ocean grid

The area of the ocean grid and the sum of the areas of the corresponding
ocean grids should match, although the coordinate systems of the
atmospheric model and the ocean model are different (the surface areas
of the earth in the atmospheric model and the ocean model do not match
exactly).

When creating the conversion file, the grid of the atmospheric model is
divided into small areas, and the area of the corresponding ocean grid
is estimated from the sum of these areas, so they do not match exactly.
For this reason, the flux balance between the atmosphere and the ocean
is adjusted by multiplying by the ratio (\(ROCN\)). The wind stresses to
the ocean are also calculated as wind stresses over sea level (\(TXO\),
\(TYO\)) and over sea ice (\(TXI\), \(TYI\)), but without multiplying
the weights of sea level and sea ice area.

\begin{eqnarray} TXO^{OGCM}(LO)=RU(LO)*ROCN(LO)*\sum_{N=1}^{IJA(LO)} \frac{[TXO^{oc}(IJC2O(LO,N))*SATM(LO,N)]}{SATMG(LO)} + RV(LO)*ROCN(LO)*\sum_{N=1}^{IJA(LO)}\frac{[TYO^{oc}(IJC2O(LO,N))*SATM(LO,N)]}{SATMG(LO)} \end{eqnarray}

\begin{eqnarray} TYO^{OGCM}(LO)=-RV(LO)*ROCN(LO)*\sum_{N=1}^{IJA(LO)} \frac{[TXO^{oc}(IJC2O(LO,N))*SATM(LO,N)]}{SATMG(LO)} + RU(LO)*ROCN(LO)*\sum_{N=1}^{IJA(LO)}\frac{[TYO^{oc}(IJC2O(LO,N))*SATM(LO,N)]}{SATMG(LO)} \end{eqnarray}

where,

\(RU(LO)\)：ベcosine of the rotation angle of the vector

\(RV(LO)\)：sine of the rotation angle of the vector

\hypertarget{redistribution-of-fluxes-in-the-ocean-model}{%
\subsubsection{Redistribution of fluxes in the ocean
model}\label{redistribution-of-fluxes-in-the-ocean-model}}

The fluxes converted to the ocean grid are updated at each time step of
the coupling. Since the coupling time step is longer than the ocean
model time step, the sea level/sea ice area ratio in the ocean model is
updated to a different value than the one used to calculate the flux.
Therefore, in order to obtain an accurate heat and water balance, the
fluxes need to be distributed according to the updated sea surface and
sea ice area ratios. The fluxes \(FLUXOA\) and \(FLUXIA\) at sea surface
and sea ice surface are ocean grid-averaged values. Fluxes to each sea
ice category are currently distributed evenly independent of sea ice
thickness.

\begin{eqnarray} FLUXIAM(L)=FLUXIA*AIM(L)\end{eqnarray}

\begin{eqnarray} FLUXOA=FLUXOA+FLUXIA*[1.0-\sum_{L=1}^{LMAX}AIM(L)]\end{eqnarray}

where, \(AIM\) denotes the percentage of area covered by sea ice in the
grid (sea ice concentration), \(L\) denotes the type of sea ice
thickness category, and \(LMAX\) denotes the number of thickness
categories. If there is no sea ice surface, all fluxes will be at sea
surface. If sea ice disappears in the middle of the coupling time step,
the flux due to sublimation is divided into the heat flux assuming a sea
ice surface and the freshwater flux (sea ice loss). The heat flux is
directly reflected in the temperature change of the first layer of
ocean. On the other hand, the freshwater flux due to sublimation is
converted into heat flux and freshwater flux and given to the first
layer of the ocean, assuming that sea ice is generated by the
sublimation. As for the wind stress, it is not weighted by sea level and
sea ice area before the grid transformation, so it is driven by the
respective area weights in each sea ice thickness category in the ocean
model. For this reason, momentum is not conserved.

\hypertarget{water-runoff-from-rivers-to-the-ocean}{%
\subsubsection{Water runoff from rivers to the
ocean}\label{water-runoff-from-rivers-to-the-ocean}}

At the end of the river model, we calculate the water flowing from the
estuary of river to the ocean. Water arriving at the estuary of the
river grid is first converted to the atmospheric sea surface grid and
time integrated in a flux coupler. After that, it is converted to the
ocean grid via an exchanger and passed to the ocean model in the same
way as the atmospheric precipitation data. At this point, the
temperature of the river water is treated as the same as the sea surface
temperature, as is the case with precipitation. Therefore, strictly
speaking, heat is not conserved. Ice runoff is handled in the same way
as snowfall.

\hypertarget{number-of-divisions-in-the-sea-surface-grid-and-resolution-of-the-ocean-model}{%
\subsubsection{Number of divisions in the sea surface grid and
resolution of the ocean
model}\label{number-of-divisions-in-the-sea-surface-grid-and-resolution-of-the-ocean-model}}

The sea surface grid is created by dividing the latitude and longitude
of the atmospheric grid, but if the number of divisions is not
sufficient and the ocean model grid has a higher resolution than the
atmospheric sea surface grid, the structure of the atmospheric grid size
may remain when the flux is converted to the ocean grid through the
exchanger. . In addition, data such as precipitation from the atmosphere
is not interpolated when converting from the atmospheric grid to the
ocean grid, so the atmospheric grid structure remains in the ocean grid
for these fluxes. When linear interpolation is used instead of cubic
spline interpolation when converting to the sea surface grid, the
atmospheric grid structure may remain for differential quantities such
as wind stress curl.
